---
title: "Summary"
output: html_document
---

# Introduction
The datasets we are using are useful in exploring our domain of interest in the carbon footprint of human activities impacting the environment of the Pacific Northwest. The first dataset is about greenhouse gases in the transportation sector, which is collected by the EPA annually. This dataset shows how much carbon dioxide is released into the atmosphere per year by different categories (fossil fuels, fluorinated gasses, etc). The other dataset we found important to exploring our domain of interest is about electric vehicles in Washington State, collected by the Washington Department of Licensing. This dataset is important because it has information on the amount of electric vehicles being registered. These datasets are useful in learning how vehicles impact our local environment of the Pacific Northwest, and exploring the idea that changing towards electric vehicles could reduce this impact of carbon emission. 

# Summary

We made charts highlighting important information calculated from our data. First and foremost, knowing that there are 82585 electric vehicles registered is a good start because we can look at how that has changed over the years, where those vehicles are, and when they were made. Then, looking at the 15 different attributes is useful, although not all attributes were used in our charts, every attribute tells us a lot of information, like make and model year, county the car was registered, and what type of electric car they are; battery, plug-in hybrid, etc. Next we calculated the most expensive model of vehicle in the dataset, being a 918 SPYDER. Looking at the price of cars is extremely important, because it is something everyone looks at when purchasing a vehicle. What was found was that in the case of many of these vehicles, the higher range of the vehicle, the higher the price. We need to look at these variables if the goal for the future is to have everyone driving electric vehicles, and if that is attainable for the average person. Finally, in our summary info we calculated the minimum and maximum model year of the cars registered in this dataset, which were 1993 to 2022. This information is important because we need to look at the trends of vehicles being registered and if the the number of registered electric vehicles is rising. 

## Aggregate Table

### Washington Electric Vehicles

```{r echo=FALSE}
library("knitr")
source("table-of-summary-information.R")

kable(full_electric_vehicle_population, caption = 'Electric Vehicle in Washington State')

```
This table containing 5 example rows of data shows how an electric vehicle's range is proportional to its base MSRP (price). However, the data shows that there are diminishing returns as price gets to higher levels.

### Greenhouse Gasses

```{r echo=FALSE}
library("knitr")
source("table-of-summary-information.R")

kable(greenhouse_gas_emissions, caption = 'US Transportation Greenhouse Gas Emissions By Year')

```

This table containing 5 rows of the most recent years shows how total US greenhouse gas emissions due to transportation has been increasing year over year.

## First Chart
```{r echo=FALSE}
library("knitr")
source("first-chart.R")

co2_over_year
```
This line graph show the carbon dioxide released by the transportation sector from 1990 to 2019. Its intended to show the trend of gas emission by year in the United States. We could observed how the trend is increasing in general as more automotive vehicle been use throughout the year. However, there are significant decreases between 2008 to 2014 in gas emission indicating less carbon dioxide release in the transportation sector.

## Second Chart

```{r echo=FALSE}
library("knitr")
source("second-chart.R")

qplot(Electric_Vehicle_Population_Data$`Model Year`, geom = "histogram", xlab = "Model Year", ylab = "Number of Electric Vehicles", main = "Number of Electric Vehicles by Model Year in Washington State")
```

This chart has the intention of displaying the number of electric vehicles in Washington state by model year of the vehicles. What is demonstrated is that many more electric vehicles are being produced and purchased in more recent years. 

## Third Chart

This [Electric Vehicle Population Data](https://data.wa.gov/Transportation/Electric-Vehicle-Population-Data/f6w7-q2d2) was provided by the State of Washington. It contains information about fully-electric and hybrid-electric cars registered in Washington State

```{r echo=FALSE}
source("third-chart.R")

ggplot(full_electric_vehicle_population, aes(x=Base.MSRP, y=Electric.Range)) + geom_point()
```

This chart was intended to show the relationship between electric vehicle range and their base MSRPs. The chart shows that there is a linear proportional relationship between the two variables; as electric vehicle range goes up, price also goes up.
