---
title: "R Notebook"
output: html_document
---

# Report Summary

## First Chart

## Second Chart

```{r echo=FALSE}
library("knitr")
source("second-chart.R")

qplot(Electric_Vehicle_Population_Data$`Model Year`, geom = "histogram", xlab = "Model Year", ylab = "Number of Electric Vehicles", main = "Number of Electric Vehicles by Model Year in Washington State")
```

This chart has the intention of displaying the number of electric vehicles in Washington state by model year of the vehicles. What is demonstrated is that many more electric vehicles are being produced and purchased in more recent years. 

## Third Chart

This [Electric Vehicle Population Data](https://data.wa.gov/Transportation/Electric-Vehicle-Population-Data/f6w7-q2d2) was provided by the State of Washington. It contains information about fully-electric and hybrid-electric cars registered in Washington State

```{r echo=FALSE}
library("knitr")
source("table-of-summary-information.R")

kable(full_electric_vehicle_population, caption = 'Electric Vehicle in Washington State')

```

This table containing 5 example rows of data shows how an electric vehicle's range is proportional to its base MSRP (price). However, the data shows that there are diminishing returns as price gets to higher levels.

```{r echo=FALSE}
source("third-chart.R")

ggplot(full_electric_vehicle_population, aes(x=Base.MSRP, y=Electric.Range)) + geom_point()
```

This chart was intended to show the relationship between electric vehicle range and their base MSRPs. The chart shows that there is a linear proportional relationship between the two variables; as electric vehicle range goes up, price also goes up.
