---
title: "R Notebook"
output: html_document
---

# Introduction
  The datasets we are using are useful in exploring our domain of interest in the carbon footprint of human activities impacting the environment of the Pacific Northwest. The first dataset is about greenhouse gases in the transportation sector, which is collected by the EPA annually. This dataset shows how much carbon dioxide is released into the atmosphere per year by different categories (fossil fuels, fluorinated gasses, etc). The other dataset we found important to exploring our domain of interest is about electric vehicles in Washington State, collected by the Washington Department of Licensing. This dataset is important because it has information on the amount of electric vehicles being registered. These datasets are useful in learning how vehicles impact our local environment of the Pacific Northwest, and exploring the idea that changing towards electric vehicles could reduce this impact of carbon emission. 

# Summary

## First Chart

## Second Chart

```{r echo=FALSE}
library("knitr")
source("second-chart.R")

qplot(Electric_Vehicle_Population_Data$`Model Year`, geom = "histogram", xlab = "Model Year", ylab = "Number of Electric Vehicles", main = "Number of Electric Vehicles by Model Year in Washington State")
```

This chart has the intention of displaying the number of electric vehicles in Washington state by model year of the vehicles. What is demonstrated is that many more electric vehicles are being produced and purchased in more recent years. 

## Third Chart

This [Electric Vehicle Population Data](https://data.wa.gov/Transportation/Electric-Vehicle-Population-Data/f6w7-q2d2) was provided by the State of Washington. It contains information about fully-electric and hybrid-electric cars registered in Washington State

```{r echo=FALSE}
library("knitr")
source("table-of-summary-information.R")

kable(full_electric_vehicle_population, caption = 'Electric Vehicle in Washington State')

```

This table containing 5 example rows of data shows how an electric vehicle's range is proportional to its base MSRP (price). However, the data shows that there are diminishing returns as price gets to higher levels.

```{r echo=FALSE}
source("third-chart.R")

ggplot(full_electric_vehicle_population, aes(x=Base.MSRP, y=Electric.Range)) + geom_point()
```

This chart was intended to show the relationship between electric vehicle range and their base MSRPs. The chart shows that there is a linear proportional relationship between the two variables; as electric vehicle range goes up, price also goes up.
